A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-02 02_Materials_and_Methods.Rmd
about the definition of macroregions

11. Defining macroregions. **TODO**

>>>>

11. Defining macroregions to observe the development of *burial type* and *burial construction* within sensible geographical and cultural units that are appropriate to the amount of available data. The regions are circular and were delimited semiautomatically by creating a regular grid in accordance to main cultural-historical regions of the european Bronze Age (**citation**). The regions have a radius of 240km and overlap slightly (Figure **TODO**). That means some graves are counted towards not just one but two regions.
